Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-10-29 forecast/paper/supplement-text.tex
add comparison to hub to the supplement, ready for Ryan

>>>>

\section{Comparing with the COVID-19 Forecast Hub}

Since July of 2020, a number of teams have been submitting real time forecasts
to the COVID-19 Forecast Hub \cite{ForecastHub}. While a number of forecast
targets can be submitted, the most related to that used in this paper---the
7-day trailing average of COVID-19 case incidence rates at the Hospital Referral
Region---are state-level forecasts for total case incidence over an epiweek.
Essentially, for each state, teams are asked to predict the total number of
cases that will be recorded over the week from Monday to Sunday. Forecasts must
be submitted by Tuesday for the current Sunday as well as the next three
Sundays. This corresponds to producing forecasts for 5, 12, 19, and 26 days
ahead. Some teams choose to submit their forecasts a few days earlier, but
always for the same targets.

To properly compare the models presented in this paper with those submitted to
the Hub, we limit ourselves to the same set of forecast dates and states, and
we predict case incidence over a week by: (1) predicting the 7-day trailing
average case rate (as in the manuscript);
(2) multiplying by 7 to give the total over a week; (3) multiplying by the state
population as reported in the 2019 US Census Population Estimate (available in
the Covidcast R package \cite{CovidcastR}). Finally, we perform the same
evaluations as in the manuscript Figure 3 and also using geometric mean as
described above. The result is shown in Figure \ref{fig:compare-to-hub}. Since
not all teams submitted forecasts to the Forecast Hub for the entire period, we
only display those which submitted for at least 6 weeks. By both metrics,
the models examined in this paper are competitive with the top teams, even
beating the Ensemble for large target horizons.

### 2021-10-29 forecast/paper/supplement.Rmd
add comparison to hub to the supplement, ready for Ryan

>>>>

<!-- Comparison to the Hub -->

```{r compare-to-hub, fig.cap="Performance of our models re-estimated for state-level, epiweek case incidence. Our models are colored the same as before. The solid light-blue line is the COVIDhub Ensemble forecast. The thin grey lines are the forecasts of other teams."}

knitr::include_graphics("fig/compare-states-to-hub.pdf")
```

### 2021-10-29 forecast/paper/supplement.tex
add comparison to hub to the supplement, ready for Ryan

>>>>

{\centering \includegraphics[width=\textwidth]{fig/compare-states-to-hub}

\caption{Performance of our models re-estimated for state-level, epiweek case incidence. Our models are colored the same as before. The solid light-blue line is the COVIDhub Ensemble forecast. The thin grey lines are the forecasts of other teams.}\label{fig:compare-to-hub}
\end{figure}
